\section{Acknowledgements}

\noindent

\normalsize

I owe this thesis to a great many people and groups. 

Firstly, to the University of Edinburgh, and the wider SOFI CDT community, I thank you. The support and community I was given from the members of the University of Edinburgh will always be a fond part of my life. The wider SOFI-CDT community as well is one I cherish, particularly cohort 2 (best cohort).

I'd like to thank my Professors, particularly Vasileios for never giving up on me even when I made it difficult. With your help my thesis transformed from something I felt incredible guilt about, to something I have found pride in. From the research group I would also like to thank Teun and John, both of whom inspired me during and afterwards.

I would also like to thank the Edinburgh Innovations student enterprise team. Your unflinching belief in me helped to build myself back up from my lowest point and gave me the support I needed to persevere, and the strength required to slay this PhDragon.

Also I would like to thank the ss13 community, you showed me the value I had in coding and developing complex systems, a skill I otherwise not have realised. And to the growing community around Whimsylabs, thank you for supporting me and believing in me.

To my family, friends and partners, I thank you for supporting my chaotic self as I muddled through my PhD, and only offered support instead of judgement. To those who body doubled me, you made this thesis a reality. To my life long friend Alex, I would like to thank you specifically, as you not only gave me a home and a space to write this, you were by my side through this challenge right from the beginning. 